Hire Ed: Job Market Dynamics for Tenure-Track Faculty Positions in Archaeology

### 2025-07-09 analysis/paper/article.qmd
out-width in the quarto chunk is the key to controlling png figure sizes in the docx

@@

# get the dat
# 2021-22 and 2022-2023
current_user_tbl <-
map(
urls_for_each_year[1:9],
~.x %>%
  read_html() %>%
  html_elements("p+ table td") %>%
  html_text2()
)

@@

```{r}
#| label: fig-panel-wiki-characteristics
#| fig-cap: "A: Total number of edits to each Wiki page (additions and deletions) per year. B: Number of unique editors, as represented by distinct usernames or IP addresses (recorded for editors without usernames), active per year. C: Active periods of individual editors, the black lines connect the date of the first and last edit of all editors that were active for three months or more. D: Typical size of each edit per year, either addition or removal of text, one word is roughly 4-6 bytes. E: Distribution of the numbers of edits per job ad for each year. F: Histogram showing that the majority of editors are only active on the site for less than one year. G: Breakdown of self-reported Wiki user categories for each year."
#| fig-width: 3
#| fig-height: 2

library(cowplot)
plot_grid(
 plot_grid(
  plot_grid(p_edits_per_year,
          p_editors_per_year,
          p_median_edit_size_per_year,
          p_edit_number_per_entry_per_year,
          labels = c("A", "B", "D", "E"),
          label_size = small_base_size),
          plot_grid(p_editor_life_distr_year,
                    p_editor_life_distr,
                    rel_widths = c(2),
                    ncol = 1,
                    labels = c("C", "F"),
                    label_size = small_base_size)),
  plot_grid(how_many_people_use_the_wiki,
            labels = "G",
            label_size = small_base_size),
  rel_heights = c(2,1),
  ncol = 1)
```

@@

```{r, fig.width = 1, fig.height = 1}
#| label: fig-show-basic-plots
#| fig-cap: "A: total number of job ads from US institutions posted to the Academic Jobs Wiki for Archaeology in each year, with coloured sections showing the proportion of jobs by title and rank. B: Ratio of tenure-track to non-tenure-track positions over time. The red line indicates a 1:1 ratio of tenure-track to non-tenure-track positions, bars taller than that line indicate more tenure-track than non-tenure-track positions in that year"
#| fig-width: 1
#| fig-height: 1

>>>>

# download the wiki pages so we can have them locally, in case they get deleted or heavily modified
walk(
urls_for_each_year[1:9],
~.x %>%
  read_html() %>% 
  xml2::write_xml(., paste0("analysis/data/raw_data/", basename(.x), ".html")))

@@

# get the data
# 2021-22 and 2022-2023
current_user_tbl <-
map(
urls_for_each_year[1:9],
~.x %>%
  read_html() %>%
  html_elements("p+ table td") %>%
  html_text2()
)

@@

```{r}
#| label: fig-panel-wiki-characteristics
#| fig-cap: "A: Total number of edits to each Wiki page (additions and deletions) per year. B: Number of unique editors, as represented by distinct usernames or IP addresses (recorded for editors without usernames), active per year. C: Active periods of individual editors, the black lines connect the date of the first and last edit of all editors that were active for three months or more. D: Typical size of each edit per year, either addition or removal of text, one word is roughly 4-6 bytes. E: Distribution of the numbers of edits per job ad for each year. F: Histogram showing that the majority of editors are only active on the site for less than one year. G: Breakdown of self-reported Wiki user categories for each year."
#| out-width: "3in"
#| out-height: "2in"

library(cowplot)
p_wiki <- 
plot_grid(
 plot_grid(
  plot_grid(p_edits_per_year,
          p_editors_per_year,
          p_median_edit_size_per_year,
          p_edit_number_per_entry_per_year,
          labels = c("A", "B", "D", "E"),
          label_size = small_base_size),
          plot_grid(p_editor_life_distr_year,
                    p_editor_life_distr,
                    rel_widths = c(2),
                    ncol = 1,
                    labels = c("C", "F"),
                    label_size = small_base_size)),
  plot_grid(how_many_people_use_the_wiki,
            labels = "G",
            label_size = small_base_size),
  rel_heights = c(2,1),
  ncol = 1)

ggsave(plot = p_wiki,
       filename = here("analysis",
            "figures", 
            "fig-panel-wiki-characteristics.png"),
       bg ="white",
       h = 5, # experiment with h and w to get the right size and proportion 
       w = 7,
       units = "in",
       dpi = 900) # make the image nice and crisp

# show figure from PNG file
knitr::include_graphics(here("analysis",
            "figures", 
            "fig-panel-wiki-characteristics.png"))
```

@@

```{r}
#| label: fig-show-basic-plots
#| fig-cap: "A: total number of job ads from US institutions posted to the Academic Jobs Wiki for Archaeology in each year, with coloured sections showing the proportion of jobs by title and rank. B: Ratio of tenure-track to non-tenure-track positions over time. The red line indicates a 1:1 ratio of tenure-track to non-tenure-track positions, bars taller than that line indicate more tenure-track than non-tenure-track positions in that year"
#| out-width: "2in"
#| out-height: "2in"
